---
title: "Course Schedule"
subtitle: "BMC201 - Web Technology"
sidebar: false
toc: false
format:
  html:
    page-layout: full
    toc: false
---

```{r packages-data, include=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)

if (requireNamespace("targets", quietly = TRUE)) {
	withr::with_dir(here::here(), {
		schedule_nested <- targets::tar_read(schedule_page_data)
		targets::tar_load(schedule_ical_file)
	})
} else {
	source(here::here("R", "tar_calendar.R"))
	schedule_nested <- build_schedule_for_page(here::here("data", "schedule.csv"))

	schedule_ical_file <- "files/schedule.ics"
}

base_url <- yaml::read_yaml(here::here("_quarto.yml"))$website$`site-url`
ical_url_absolute <- paste0(base_url, "/", schedule_ical_file)
```

Here's your roadmap for the semester!

- [**Lectures**](/lectures/index.qmd) ({{< fa desktop >}}): Lecture materials for each class session.

- [**Content**](/content/index.qmd) ({{< fa book-open-reader >}}): This page contains lecture materials, readings, and videos for each topic. Read and watch these.

- [**Labs**](/labs/index.qmd) ({{< fa flask >}}): Hands-on lab exercises with step-by-step instructions (3-hour sessions weekly).

- [**Assignments**](/assignment/index.qmd) ({{< fa pen-ruler >}}): Regular assignments with due dates. Complete these to practice what you've learned.

- [**Quizzes**](/quiz/index.qmd) ({{< fa list-check >}}): Use pre-class quizzes to quickly check understanding before lecture delivery.

- [**Resources**](/resource/index.qmd) ({{< fa books >}}): Additional learning materials and references.

::: {.callout-tip}
## Subscribe

You can subscribe to this calendar URL in Outlook, Google Calendar, or Apple Calendar.

::: {.grid .align-items-center}

::: {.g-col-12 .g-col-md-3}
<p class="download-btn"><a class="btn btn-danger" href="/`r schedule_ical_file`" role="button">{{< fa calendar-alt >}} Download ICS</a></p>
:::

::: {.g-col-12 .g-col-md-9 .subscribe-url}
<p><input class="form-control" type="text" value="`r ical_url_absolute`" onclick="this.select()" readonly></p>
:::

:::
:::

```{r build-table, include=FALSE}
show_table <- function(group_id) {
	cat(glue::glue("\n\n<div class=\"schedule-group\"><div class=\"schedule-group-title\"><h3>{schedule_nested$group[[group_id]]}</h3></div>\n"))

	tbl <- schedule_nested$data[[group_id]] |>
		kbl(escape = FALSE, align = "rlccccc", table.attr = 'class="schedule-table"') |>
		kable_styling() |>
		column_spec(1, width = "18%", extra_css = "padding-right: 20px; white-space: nowrap;") |>
		column_spec(2, width = "42%") |>
		column_spec(3:7, width = "8%")

	cat(tbl)
	cat("</div>")
}
```

```{r show-table, echo=FALSE, results="asis"}
walk(seq_len(nrow(schedule_nested)), ~show_table(.x))
```

